Resurgence of the Airy function

### 2022-05-14 airy-resurgence.tex
Clean up sketch of higher Airy coefficients

\left[ z^{n-1} \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{n-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z \big({-}\tfrac{\partial}{\partial z}\big) - c_0 \right] \varphi = 0,

@@

or equivalently
\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z^{3-n} \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z^{2-n} \big({-}\tfrac{\partial}{\partial z}\big) - c_0 z^{1-n} \right] \varphi = 0,

>>>>

\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] \varphi = 0.

@@

The sub-leading coefficients are the triangular numbers
\[ c_n^{(1)} = \frac{n(n-1)}{2}. \]
\color{DarkCyan}
The later coefficients can be written as\footnote{Many thanks to Peter Taylor for noticing this [\url{https://mathoverflow.net/q/422337/1096}].}
\[ c_n^{(k)} = \frac{b_n^{(k)}}{n^k}\,(n+1)^{\underline{k+2}} \]
in terms of the polynomials
\begin{equationarray*}{*{11}{c}}
b_n^{(2)} & = & \tfrac{1}{24} \\
b_n^{(3)} & = & \tfrac{1}{48} n \\
b_n^{(4)} & = & \tfrac{73}{5760} n^2 & + & \tfrac{1}{1152} n & - & \tfrac{1}{2880} \\
b_n^{(5)} & = & \tfrac{11}{1280} n^{3} & + & \tfrac{1}{768} n^{2} & - & \tfrac{1}{1920} n \\
b_n^{(6)} & = & \tfrac{3625}{580608} n^{4} & + & \tfrac{61}{41472} n^{3} & - & \tfrac{181}{322560} n^{2} & - & \tfrac{1}{41472} n & + & \tfrac{1}{181440}. \end{equationarray*}
Searching for 580608 in the OEIS turns up the leading coefficients $\beta^{(k)}$ of these polynomials, which are listed as {\tt A249276} and {\tt A249277}. They're defined by the identity [Yang, ``Approximations for Constant $e$ and Their Applications'']
\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{\beta^{(2)}}{n^2} - \frac{\beta^{(3)}}{n^3} - \frac{\beta^{(4)}}{n^4} - \frac{\beta^{(5)}}{n^5} - \ldots, \]
which tells us that
\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{b_n^{(2)}}{n^2} - \frac{b_n^{(3)}}{n^4} - \left[\frac{b_n^{(4)}}{n^6} + o\left(\frac{1}{n^5}\right)\right] - \left[\frac{b_n^{(5)}}{n^8} + o\left(\frac{1}{n^6}\right)\right] - \ldots. \]
The last coefficient can be written as
\[ c_n^{(n-1)} = \left(\frac{n-1}{n}\right)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}}, \]
giving
\[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ (n+1)^{\underline{n+1}}. \]
